%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.1 (9/1/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry

\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-red} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------
\name{Saksham}{Sharma}
% \address{E-255, Hall 2, Indian Institute of Technology Kanpur, Kanpur,
% 208016}
\address{Indian Institute of Technology Kanpur}
\mobile{(+91) 7755-05-8004}

\email{saksham0808@gmail.com}
\homepage{sakshamsharma.com}
\github{sakshamsharma}
\linkedin{saksham-sharma}
%\skype{skypeid}
%\stackoverflow{SOid}{SOname}
%\twitter{@twit}

\position{Third Year Undergraduate{\enskip\cdotp\enskip}Computer
  Science and Engineering} % Your expertise/fields
%\quote{``Make the change that you want to see in the world."} % A
%quote or statement

\makecvfooter{\today}{Saksham Sharma~~~·~~~Résumé}{\thepage} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed
%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{}{VMWare, Palo Alto} % The company being applied to

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{VMWare: Intern application for Launch - R\&D Undergraduate Summer Intern Program} % The title of the letter

\letteropening{} % How the letter is opened

\letterclosing{Sincerely,} % How the letter is closed

% \letterenclosure[Attached]{} % Any enclosures with the letter

%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

\makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}

%------------------------------------------------

  \lettersection{About Me}
  I am a 3rd year undergraduate at the Indian Institute of Technology
  Kanpur, majoring in Computer Science and Engineering, applying for a
  R\&D Undergraduate Intern position for the Summer of 2017.

  I am the Institute Rank 1 at my university, with a CGPA of
  10.0/10.0, and have won numerous awards; all this while being
  heavily invested in programming and computer science all along. I
  was a Research Fellow at the Max Planck Institute for Software
  Systems in Germany this summer.

  Additionally, I have significant experience with multiple
  programming languages, technologies, and Linux, and am comfortable
  picking up things on the go, which I like to call the `hacker'
  mentality. I keep a blog of all my ideas, things I've learnt,
  networking, programming and computers in general at
  http://acehack.org. Also, I occasionally contribute to Open Source,
  and maintain some my own well appreciated open source projects and
  tools on Github.

  \lettersection{Past Experience}
  I have worked on multiple projects with faculty, with varying degree
  of research.

  My most recent project involves making a completely mobile and
  connectionless implementation of video chatting over UDP. Being a
  from-scratch project, it involves some bold moves away from
  conventional protocols.

  My first networks idea, a simple proxy to wrap arbitrary network
  traffic in HTTP packets (to bypass HTTP proxy restrictions) received
  considerable attention on Github, staying in the top 5 C++ trending
  on Github for two days.

  Also, I've designed and am coding a platform for completely
  anonymous and zero-server-trust based couple matching algorithm, to
  be used on my campus.

  I have worked in a small team on a large scale web platform in Scala
  as well, where I designed and implemented the complete search
  infrastructure, and got acquainted with industry coding practices
  and team development.

  \lettersection{Motivation}
  I have been marveling at virtualization ever since I was introduced
  to it, and have recently realized the technical challenges associated
  with the same. This in fact has been among the top reasons why I wish
  to work at VMWare.

  Given this, and my passion for working in Systems, I believe that a
  chance to work at VMWare for the summers, and that too in an R\&D
  position during my undergraduate would be the best I can hope for,
  and I am confident that given a chance, I shall be able to prove my
  worth, and more.

  Thank you for taking the time to consider my application.


\end{cvletter}

%----------------------------------------------------------------------------------------

\makeletterclosing % Print the signature and enclosures

\end{document}
%%% Local Variables:
%%% mode: latex
%%% End:
