\documentclass[11pt,a4paper]{moderncv}
\usepackage{multicol}           %% allows to create more than two columns
\usepackage{array}              %% for adjusting column widths in table
\usepackage{color}
\usepackage{lipsum}
\usepackage{enumitem}

\ifdefined\onep
  \usepackage[margin=0.50in, top=0.2in,bottom=0.3in]{geometry}
\else
  \usepackage[margin=0.25in, top=0.13in,bottom=0.3in]{geometry}
\fi

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\setlength{\parindent}{0pt}	%% used for setting the no indentation at the beginning of paras

\setlist{nosep}
\pagenumbering{gobble}

% modern themes
\moderncvstyle{banking}
\moderncvcolor{blue}
\moderncvicons{awesome}
\definecolor{titleblue}{RGB}{20,20,100}

\newcommand{\experience}[4]{
\vspace{0.1cm}
\item \textbf{\large{#1}} \emph{#2} \hfill \textit{#3}
  \begin{itemize}[leftmargin=*]
    \setlength\itemsep{0em} #4
  \end{itemize}
}

\newcommand{\education}[5]{
\item[] \textbf{\large{#1 :}} #2 - \emph{#3: \textbf{#4}} \hfill\textit{#5}
}

\newcommand{\onepage}[1]{
\ifdefined\onep
#1
\fi
}

\newcommand{\twopage}[1]{
\ifdefined\twop
#1
\fi
}

\newcommand{\secspace}{
\onepage{\vspace{-0.27cm}}
\twopage{\vspace{-0.1cm}}
}

\newcommand{\secbelow}{
\onepage{\vspace{-0.07cm}}
}

%% Personal data
\firstname{Saksham}
\familyname{Sharma}
\address{Computer Science and Engineering}{IIT Kanpur} 
\email{saksham0808@gmail.com}
\ifdefined\twop
  \extrainfo{\emailsymbol\emaillink{sakshams@(cse).iitk.ac.in}}
\fi
\social[github]{sakshamsharma}
\homepage{http://acehack.org}

\begin{document}
\maketitle
\onepage{\vspace{-1.4cm}}
\twopage{\vspace{-1cm}}
\section*{Educational Qualifications}
\secbelow
\begin{itemize}
  \twopage{\setlength\itemsep{0.2cm}}
  \education{Bachelor of Technology}{Indian Institute of Technology Kanpur}{CPI}{10.0/10.0}{July'14-Present}
  \education{Senior Secondary - CBSE}{D.A.V. Public School, Amritsar}{Overall percentage}{97.6\%}{2014}
  \education{Secondary - CBSE}{D.A.V. Public School, Amritsar}{Overall grade}{10.0/10.0}{2014}
\end{itemize}

\secspace
\section*{Academic Achievements and Scholarships}
\secbelow
\begin{itemize}
  \twopage{\setlength\itemsep{0.5em}}
  \item All India Rank \textbf{10} in Joint Entrance Exam Mains 2014 among 1.5 million candidates              \hfill \textit{2014}
  \item All India Rank \textbf{138} in Joint Entrance Exam Advanced 2014 among 150,000 candidates            	\hfill \textit{2014}
  \item Aditya Birla Group Scholarship recipient, awarded to 15 IIT freshmen. \hfill \textit{2014}

  \twopage{
  \item Kishore Vigyanik Protsahn Yojna (KVPY) Scholar, Dept of Science and Technology, Govt of India
    \hfill \textit{2013}
  \item National Talent Search (NTSE) Scholar, organized by NCERT, Govt\ of India
    \hfill \textit{2010}}

  \onepage{\item Kishore Vigyanik Protsahn Yojna (KVPY), National Talent Search awardee.\hfill\textit{2013,10}}

  \twopage{
    \item Qualified National Standard Examination in Physics (NSEP for Class 12) in grade 11 and 12 \hfill \textit{2012-13}
    \item Selected for INSPIRE Scholarship Scheme (Dept of Science and Technology, Govt of India). \hfill \textit{2014}}

\end{itemize}

\secspace
\section*{Projects}
\secbelow
\begin{itemize}
  \twopage{\setlength\itemsep{0.5em}}
\experience{Web Developer}{IIT Kanpur}{May'2015-Present}{
    \item Working on a scaleable web-app using Haskell, Scala with Akka, ElasticSearch, Node.js, Dart, Angular.
    \item Worked on the backend and the frontend team, and handled an independent division of the app as a full-stack Web Developer.
    }

\experience{Microsoft code.fun.do 2014 and 2015}{Winning team member twice}{Jan'2015 and Sep'2016}{
    \item \textit{Fresher} Designed a graphing app to plot implicit 2D mathematical functions for Windows Phone.
    \item \textit{Sophomore} Made a frontend to an open source program simulation code for Microsoft Windows.
    }

\experience{ABU Robocon 2015}{Supervisor: Prof. Bhaskar Dasgupta}{Oct'2014-Mar'2015}{
    \item Worked on making 2 semi-autonomous robots capable of playing badminton on a full court.
    \item Image-processing to track the shuttle, predict trajectory. Used Arduino and Odroid for robot control.
    \item Used stereo-vision, and later Microsoft Kinect to source depth data.
    }

\experience{Microsoft code.fun.do Finalists Forum 2015}{National 5th in Coding Milestone}{May'2015-Jul'2015}{
    \item Developed an app to help users learn programming in their spare time.
    \item An extensive app in C\# and backend Online Judge in Node.js to run and verify user submitted programs.
    }
    \end{itemize}

\secspace
\section*{Work and Volunteer Experience}
\secbelow
\begin{itemize}
  \twopage{\setlength\itemsep{0.5em}}
    \experience{Development Intern}{under DoFA IIT Kanpur, Prof. Manindra Agarwal}{May'15-July'15}{
      \item Was adjudged as one of the best interns as a freshman.
      \item Worked on a scaleable web application with a large technology stack.
      }

    \experience{Secretary}{Programming Club, IIT Kanpur}{Apr'15-Present}{
      \twopage{
      \item Organized Freshers' Programming Contest, setting and testing algorithmic questions.
      \item Organized beginner programming workshops for students.
      }
      \onepage{
      \item Organized Freshers' Programming Contest and beginner programming workshops.
      }
    }

    \experience{Technical Secretary}{Association for Computing Activities, IIT Kanpur}{Aug'15-Present}{
      \item Member of student body of CSE department, IIT Kanpur
      }
      
    \twopage{
      \experience{Student Guide}{Counselling Service, IIT Kanpur}{July'15-Present}{
        \item Helped 9 students adjust to the rigours of college life, by providing emotional support along with counselling.
        \item Assisted in the Orientation Programme '15 for the fresher batch.
      }
    }

\end{itemize}

\secspace
\section*{Technical Skills}
\secbelow
\begin{tabular}{L{0.05cm} L{5cm} l}
  &Web Development 	          &Node.js (with Express), Scala (with Akka), Javascript, Dart, PHP, Angular\\
  &Programming Languages      &C/C++, Python, Haskell, Java, C\#, Scala\\
  &Operating Systems	        &Gentoo Linux, Arch Linux, Microsoft Windows, Ubuntu\\
  &Utilities                  &Vim, Git, GDB, Shell Scripting, Visual Studio, GNU Octave, OpenCV, \LaTeX\\
  &Platforms                  &Windows Phone, Microsoft Kinect, Arduino
\end{tabular}

\secspace
\section*{Relevant Courses}
\secbelow
\begin{tabular}{L{0.05cm} L{6.2cm} L{6.5cm} L{7.5cm} L{8cm} L{13cm}}
  & Introduction to Programming(A*)  & Logic in Computer Science & Abstract Algebra\\
& Discrete Mathematics             & Data Structures and Algorithms(**) & Computer Organization(**)\\
& Probability and Statistics (**)  & Computer Systems Security(**) & Linear Algebra, O.D.Es, Calculus\\
  \vspace{0.2cm}
& \footnotesize{A* grade for exceptional performance}
& \footnotesize{*: Course in progress}
& \footnotesize{**: To be completed by April '16}
\end{tabular}

\secspace
\section*{Interests}
\secbelow
\begin{tabular}{L{0.05cm} L{5.8cm} L{6.5cm} L{7.5cm} L{8cm} L{13cm}}
  & Cyber Security         & Web Development       & Programming Languages\\
  & Functional Programming & Software Verification & Machine Learning
\end{tabular}

\secspace
\section*{Miscellaneous}
\secbelow
\begin{tabular}{L{0.05cm} l}
  & Sporadic blogger at my blog \url{http://acehack.org}\\
  & Occasional contributor to public Open Source projects on Github \url{https://github.com/sakshamsharma}
\end{tabular}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
