\documentclass[11pt,a4paper]{article}
%%\usepackage{showframe}        %% used to show the frames
\usepackage{blindtext}          %% creates dummy text
\usepackage{multicol}           %% allows to create more than two columns locally or globally
%\usepackage{flenqn}            %% left-alignment of formula
%\usepackage{leqno}             %% labels formula on left hand side instead of right
\usepackage{array}              %% for adjusting column widths in table
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}     %% new column type
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}       %% new column type            
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}      %% new column type
\usepackage{hyperref}
\setlength{\parindent}{0pt}	%% used for setting the no indentation at the beginning of the paragraph
\usepackage{lipsum}
\usepackage{enumitem}
\setlist{nosep}
%\setlist{nolistsep}                          %% no space before itemize
\usepackage{enumitem}                        %% for eliminating space before itemize
\usepackage[margin=0.75in, top=0.8in,bottom=0.8in]{geometry}         %% page margins >0.5" and < 1.0"
\pagenumbering{gobble}

\begin{document}
\textbf{\huge{Saksham Sharma}}\\	%% to write bold and large 
Sophomore Undergraduate    \hfill Email: \texttt{saksham0808@gmail.com}\\
Computer Science and Engineering      \hfill  Email: \texttt{sakshams@iitk.ac.in}\\
Indian Institute of Technology Kanpur	\hfill Mobile: {+91-7755058004}\\


\textbf{\Large{Educational Qualification}}\\
\rule{\textwidth}{01pt}
%%	\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
\textbf{\large{Bachelor of Technology, Computer Science and Engineering}} \hfill\textit{ July'14-Present}\\
Indian Institute of Technology, Kanpur\\
Cumulative Performance Index: 10.0\\
\\
\textbf{\large{All India Senior School Certificate Examination(AISSCE) - CBSE}} \hfill\textit{ 2014}\\
Overall percentage: 97.6\%\\
D.A.V. Public School, Amritsar\\
Science Stream\\
\\
\textbf{\large{All India Secondary School Examination (AISSE) - CBSE}} \hfill\textit{ 2012}\\
Cumulative Grade Point Average(CGPA): 10\\
D.A.V. Public School, Amritsar\\

\textbf{\Large{Academic Achievements and Scholarships}}\\
\rule{\textwidth}{01pt}
\begin {itemize}
%\setlength\itemsep{0em}		%% set the separation
\item Cumulative Point Index of 10.0 after Semester I and II                                        \hfill \textit{2014-15}
\item All India Rank 138 in Joint Entrance Exam Advanced 2014 among 150,000 candidates            	\hfill \textit{2014}
\item All India Rank 10 in Joint Entrance Exam Mains 2014 among 1.5 million candidates              \hfill \textit{2014}
\item Received the Aditya Birla Group Scholarship along with 15 other IITans                        \hfill \textit{2014}
\item Received the Kishore Vigyanik Protsahn Yogna (KVPY) Scholarship with an AIR of 109            \hfill \textit{2013}
\item Received the National Talent Search Examination (NTSE) Scholarship                            \hfill \textit{2010}
\item Qualified National Standard Examination in Physics (NSEP) twice                               \hfill \textit{2012-13}
\end{itemize}

\vspace{5mm}

\textbf{\Large{Projects}}\\
\rule{\textwidth}{01.0pt}
\begin {itemize}

\item \textbf{\large{Microsoft code.fun.do Finalists Forum 2015}} \hfill\textit{ May'2015-Jul'2015}\\ \emph{5th National in Coding Milestone}
    \begin{itemize}
    \setlength \itemsep{0em}
    \item Developed an app to help users learn programming in their spare time.
    \item Made an extensive app with multiple features like lessons, scratchpad.
    \item Wrote a backend web service in Node.js to compile, run and verify user's input codes.
\\
    \end{itemize}

\item \textbf{\large{Microsoft code.fun.do 2015}} \hfill\textit{ Jan'2015}\\ \emph{Winning team member}
    \begin{itemize}
    \setlength \itemsep{0em}
    \item Designed a graphing app to plot implicit 2D mathematical functions for Windows Phone
\\
    \end{itemize}

\item \textbf{\large{ABU Robocon 2015}} \hfill\textit{ Oct'2014-Mar'2015}\\ \emph{Supervisor: Prof. Bhasker Dasgupta (IIT Kanpur)}
    \begin{itemize}
    \setlength \itemsep{0em}
    \item Worked on making 2 semi-autonomous robots capable of playing badminton on a full court.
    \item Used image-processing to track the shuttle, predicted its trajectory and moved the robot.
    \item Used Microsoft Kinect to get depth data. Also worked with stereo-vision.
\\
    \end{itemize}

\item \textbf{\large{NASA AMES Space Settlement Design Contest}} \hfill\textit{ Dec'2011-Mar'2012}\\ \emph{Team Leader}
    \begin{itemize}
    \setlength \itemsep{0em}
    \item Designed in detail a Space Settlement capable of settling 14000 permanent residents in orbit around the earth
    \item Internation 1st prize among the Grade 10 category.
\\
    \end{itemize}


\end{itemize}


\textbf{\Large{Work Experience}}\\
\rule{\textwidth}{01pt}
\begin {itemize}

\item \textbf{\large{Hackcave, IIT Kanpur NYC Office}} \hfill\textit{ May'15 - Jul'15}\\ \emph{\large{Web Development Intern}}
    \begin{itemize}
    \setlength \itemsep{0em}	 
    \item Worked on developing a scaleable web-app.
    \item Used Scala with Akka, ElasticSearch, Node.js and Dart.\\
    \end{itemize}

\item \textbf{\large{Programming Club, IIT Kanpur}} \hfill\textit{ Apr'15 - Present}\\ \emph{\large{Secretary}}
    \begin{itemize}
    \setlength \itemsep{0em}
    \item Helped organize workshops related to programming.
    \item Promoted programming culture among the fresher batch of 2015.\\
    \end{itemize}

\item \textbf{\large{Counselling Service, IIT Kanpur}} \hfill\textit{ Apr'15 - Present}\\ \emph{\large{Student Guide}}
    \begin{itemize}
    \setlength \itemsep{0em}
    \item Helped the fresher batch of 2015 settle in to college life.
    \item Helped organize the Orientation of the fresher batch, 2015.
    \end{itemize}

\end{itemize}

\vspace{5mm}

\textbf{\Large{Technical Skills}}\\
\rule{\textwidth}{01pt}
\begin{tabular}{L{0.05cm} L{5cm} l}
&Web Development 	        &HTML/CSS, Node.js, Javascript, Dart, PHP \\
&Programming Languages      &C/C++, Python, Java, C\#, Scala, Shell Scripting\\
&Operating Systems	        &Arch Linux, Ubuntu, Microsoft Windows\\
&App Development		    &Windows Phone\\
&Utilities                  &Vim, Git, Microsoft Visual Studio, GNU Octave\\
&Web Frameworks             &Node.js with Express.js and Jade, Scala with Akka, LAMP stack\\
&CAD	                	&Autodesk Inventor, 3ds\\
&Hardware                   &Microsoft Kinect, Arduino\\

\end{tabular}
\vspace{6mm}



\textbf{\Large{Relevant Courses}} \\
\rule{\textwidth}{01pt}
\begin{tabular}{L{0.05cm} L{6cm} L{5.5cm} L{5.5cm}}
& Introduction to Programming(A*)   & Introduction to Calculus        \\
& Linear Algebra                    & Ordinary Differential  Equations\\
\end{tabular}\\\\




\textbf{\Large{Other Interests}}\\
\rule{\textwidth}{01pt}

\begin {itemize}
\setlength\itemsep{0em}		%% set the separation
\item Image Processing and Parallel Processing
\item Algorithms
\item Machine Learning
\item Web Development
\item Artificial Intelligence
\end{itemize}

%%	\blindtext		%% used to print the default text at any place
\
\end{document}
