\documentclass[11pt,a4paper]{moderncv}
\usepackage[margin=0.40in, top=0.2in,bottom=0.3in]{geometry}
\usepackage{multicol}           %% allows to create more than two columns
\usepackage{array}              %% for adjusting column widths in table
\usepackage{color}
\usepackage{lipsum}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}


\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\setlength{\parindent}{0pt}	%% used for setting the no indentation at the beginning of paras

\setlist{nosep}
\pagenumbering{gobble}

% modern themes
\moderncvstyle{banking}
\moderncvcolor{blue}
\moderncvicons{awesome}
\definecolor{titleblue}{RGB}{20,20,100}

\newcommand{\experience}[4]{
  \vspace{0.1cm}
\item \textbf{\large{#1}} \textit{#2}\hfill\textit{#3}
  \begin{itemize}[leftmargin=*]
    \setlength\itemsep{0em} #4
  \end{itemize}
}

\newcommand{\experiencetwo}[4]{
  \vspace{0.1cm}
\item \textbf{\large{#1}} \hfill\textit{#3}\\\textit{#2}
  \begin{itemize}[leftmargin=*]
    \setlength\itemsep{0em} #4
  \end{itemize}
}


\newcommand{\education}[5]{
\item[] \textbf{\large{#1 :}} #2 - \emph{#3: \textbf{#4}} \hfill\textit{#5}
}


%% Personal data
\firstname{Saksham}
\familyname{Sharma}
\address{Computer Science and Engineering}{IIT Kanpur} 
\email{saksham0808@gmail.com}
\extrainfo{sakshams@(cse.)iitk.ac.in}
\extrainfo{\emailsymbol\emaillink{sakshams@(cse).iitk.ac.in}}
\social[github]{sakshamsharma}
\homepage{http://acehack.org} 

\begin{document}
\maketitle
\vspace{-1cm}
\section*{Educational Qualifications}
\begin{itemize}
  \setlength\itemsep{0.2cm}
  \education{Bachelor of Technology}{Indian Institute of Technology Kanpur}{CPI}{10.0/10.0}{July'14-Present}
  \education{Senior Secondary - CBSE}{D.A.V. Public School, Amritsar}{Overall percentage}{97.6\%}{2014}
  \education{Secondary - CBSE}{D.A.V. Public School, Amritsar}{Overall grade}{10.0/10.0}{2014}
\end{itemize}

\vspace{-0.1cm}
\section*{Academic Achievements and Scholarships}
\begin{itemize}
  \setlength\itemsep{0.5em}
\item Institute Rank \textbf{1}, IIT Kanpur (CPI 10.0/10.0 in all 4
  semesters) \hfill \textit{2014-Present}
\item All India Rank \textbf{10} in Joint Entrance Exam Mains 2014 among 1.5 million candidates              \hfill \textit{2014}
\item All India Rank \textbf{138} in Joint Entrance Exam Advanced
  2014 among 150,000 candidates            	\hfill \textit{2014}
\item Academic Excellence Award, IIT Kanpur \hfill \textit{2014-15}
\item Aditya Birla Group Scholarship recepient, awarded to 15 IIT freshmen.                        \hfill \textit{2014}
\item Kishore Vigyanik Protsahn Yojna (KVPY) Scholar, Dept of Science and Technology, Govt of India
  \hfill \textit{2013}
\item National Talent Search (NTSE) Scholarship awardee, by NCERT, Govt\ of India
  \hfill \textit{2010}
\item National top 400 in National Standard Examination in Physics in grade 11 and 12. \hfill \textit{2012-13}
\item Selected for INSPIRE Scholarship Scheme (Dept of Science and Technology, Govt of India).
  \hfill \textit{2014}

\end{itemize}

\vspace{-0.1cm}
\section*{Projects and competitions}
\begin{itemize}
  \setlength\itemsep{0.5em}
  \experiencetwo{Automated Accuracy improvement for Floating Point Expressions}{Max Planck Institute for Software
    Systems, under Dr. Eva Darulová}{May'2016-July'2016}{
    \item Developed and evaluated a tool (in Scala) to rewrite
      mathematical expressions to lower floating point errors, thus
      improve accuracy for scientific and embedded applications
    \item Obtained successful results, improving expressions by 50\%,
      tested on expressions from various sources
    \item Part of a larger tool being developed to optimize numerical
      programs
    \item Gave a talk on the same to the Programming Languages group
  }
  
  \experience{Full Stack Developer}{IIT Kanpur}{May'2015-Present}{
  \item Working on a scaleable web-app in a polyglot environment;
    using Scala with Akka, ElasticSearch, TypeScript, Node.js, Haskell, Angular2
  \item Implemented various functionalities on the backend and
    frontend, managing infra
  \item Designed a complete search functionality implemented using
    ElasticSearch, Node.js, Scala and TypeScript
  }

  \experience{Microsoft code.fun.do 2014 and 2015}{Winning team member twice}{Jan'2015 and Sep'2016}{
  \item \textit{Fresher} Designed a graphing app to plot implicit 2D mathematical functions for Windows Phone.
  \item \textit{Sophomore} Made a frontend to an open source program simulation code for Microsoft Windows.
  }

  \experience{ABU Robocon 2015}{Supervisor: Dr. Bhaskar Dasgupta}{Oct'2014-Mar'2015}{
  \item Worked on making 2 semi-autonomous robots capable of playing badminton on a full court.
  \item Image-processing to track the shuttle, predict trajectory. Used Arduino and Odroid for robot control.
  \item Used stereo-vision, and later Microsoft Kinect to source depth
    data.
  \item Finished 11th among 85 teams from all over India, at ABU Robocon
    '15, Pune
  }

  \experience{Microsoft Build The Shield 2016}{Capture The Flag
    hacking contest}{Mar'2015}{
  \item Qualified National Online round, a Capture The Flag (CTF)
    competition focused on Security and Offensive Hacking
  \item National 10th in the onsite finals at Microsoft Campus Hyderabad
  }

  \experience{Microsoft code.fun.do Finalists Forum 2015}{National 5th in Coding Milestone}{May'2015-Jul'2015}{
  \item Developed an app to help users learn programming in their spare time.
  \item Implemented a frontend app using C\# for Windows Phone
  \item Wrote backend web service (Online Judge) in Node.js to compile, run and verify user submitted programs.
  }
\end{itemize}

\section*{Work and Volunteer Experience}
\begin{itemize}
  \setlength\itemsep{0.5em}
  \experience{Development Intern}{under DoFA IIT Kanpur, Prof. Manindra Agarwal}{May'15-July'15}{
  \item Was adjudged as one of the best interns as a freshman.
  \item Worked on a scaleable web application with a large technology
    stack.
  }

  \experience{Coordinator}{Programming Club, IIT
    Kanpur}{Apr'16-Present}{
  \item Rewrote, deployed and populated Programming Club website \href{https://pclub.in}{pclub.in}
  \item Helped organize the Science and Technology Council Summer Camp
    '16
  }

  \experience{Secretary}{Programming Club, IIT Kanpur}{Apr'15-Present}{
  \item	Organized Freshers’ Programming Contest, setting and testing algorithmic questions.
  \item	Conducted beginner programming workshops for students.
  \item Promoted Linux use and Installed Linux on multiple systems during Linux Installation Fest.
  \item Organized Freshers’ Programming Contest, programming workshops and Linux Install Fest
  }

  \experience{Software Corner Manager}{Techkriti '16, IIT
    Kanpur}{Dec'15-Mar'16}{
  \item	Designed and implemented a new Esoteric Programming language based on Assembly, and hosted a national level competition on the same.
  \item	Wrote an Online Judge for a National High Performance Computing competition, hosted on CDAC’s Param Yuva II Supercomputer.
  \item	Handled logistics and organization of multiple other Software related events.
  }

  \experience{Technical Secretary}{Association for Computing Activities, IIT Kanpur}{Aug'15-Present}{
  \item	Helped in increasing familiarity of Computer Science Freshers with their department
  \item	Mentored a group of 5 students for a semester project on Introduction to Functional Programming
  }

  \experience{Student Guide}{Counselling Service, IIT Kanpur}{July'15-Present}{
  \item Helped 9 students adjust to the rigours of college life, by providing emotional support along with counselling.
  \item Organized the Orientation Programme '15 for the fresher batch.
  }

\end{itemize}


\section*{Technical Skills}
\begin{tabular}{L{0.05cm} L{5cm} l}
  &Web Development 	          &Node.js (with Express), JavaScript, Scala (with Akka), Angular\\
  &Programming Languages      &C/C++, Scala, Python, Haskell, Java,
                                Lisp, x86 Assembly\\
  &Operating Systems	        &Gentoo Linux, Arch Linux, Ubuntu, Microsoft Windows\\
  &Utilities                  &Emacs and Vim both, Git, GDB, Shell
                                Utilities and scripting in Linux, \LaTeX\\
  &Platforms                  &Windows Phone, Microsoft Kinect, Arduino\\
\end{tabular}

\section*{Relevant Courses}
% \begin{tabular}{L{0.05cm} L{6.5cm} L{7.0cm} L{8cm} L{8cm} L{12cm}}
\begin{tabular}{L{6.8cm} L{6.0cm} l}
  Data Structures and Algorithms (A*) & Computer Organization (A*)
  & Introduction to Programming (A*)\\
  Tools for Computing (A*) & Computer Systems Security (A)
  & Discrete Mathematics (A)\\
  Abstract Algebra (A) & Logic in Computer Science (A)
  & Probability and Statistics (A)\\
  \vspace{0.3cm}
  \footnotesize{A* grade for exceptional performance} & &
\end{tabular}

\section*{Interests}
\begin{tabular}{L{5.5cm} L{5.5cm} l}
  Computer Systems Security & Open Source Development
  & Programming Languages and Approximation\\
  Functional Programming & Web Development
  & Linux System administration\\
  Capture the Flag contests & &
\end{tabular}

\section*{Miscellaneous}
\begin{itemize}
  \item Sporadic blogger at my blog \url{http://acehack.org} about Linux, programming etc
  \item Occasional contributor to public Open Source projects on Github
    \url{https://github.com/sakshamsharma}.
  \item Multiple personal projects on Github, including blogs, an
    Emacs plugin, utility repositories.
  \item	Administer various servers in IIT Kanpur, including the
    community Gentoo mirror, a Gentoo-based Navya server, and the
    server VM of Programming Club. Deploy and automate services for
    campus
  \item Attended a full paper-reading seminar-like course on
    Approximate Computing during Summer ’16 at the Max Planck
    Institute, Germany
  \item A Linux Enthusiast, tinker around and tweak my Linux installation in my free time
\end{itemize}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "twopage"
%%% End:
