\documentclass{tccv}
\usepackage[english]{babel}
\usepackage{comment}
\usepackage{enumitem}

\newlist{inlinelist}{itemize*}{1}
\setlist*[inlinelist,1]{
  label={$\bullet$\hspace{0.07cm}},
}

% Why do I need this one some computers and not others?
\usepackage{fontspec} % Was able to fix it with this line
\defaultfontfeatures{Path = /home/saksham/.fonts/fontawesome/opentype/ }
\usepackage{fontawesome}

\newcommand{\linkbold}[1]{
  \textcolor{black}{\large{\textit{\textbf{#1}}}}
}

\newcommand{\astar}[0]{\small{\textit{A$*$}}}

\begin{document}

\definecolor{myred}{HTML}{801010}
{\usekomafont{part} \textit{Saksham \textcolor{myred}{Sharma}}}
\medskip\\
\large{Computer Science and Engineering}\\
{Indian Institute of Technology Kanpur}

\vspace{-0.5cm}
\section{Work Experience}
\begin{experience}
  \expitem{Software Engineering Intern}{May-Jul'17}
  {Google Seattle, GKE/Kubernetes Security Team}
  {
  \item Worked on Kubernetes, Google's Open Source \\Docker / container orchestration platform, to
    encrypt resources at rest, in cluster database (etcd).
  \item Feature required by industry for security hardening and protection of clusters.
  \item Used envelope encryption using Key-Encryption-Key and Data-Encryption-Key to allow
    using a remote root-of-trust for encryption.
  \item Allowed key rotations in a multi-master system.
  \item Feature released in v1.7, integration with Google's Cloud Key Management service upcoming.
  }

  \expitem{Summer Research Fellow}{May-Jul'16}
  {Max Plank Institute, \small{Germany}, under
  \href{http://www.mpi-sws.org/~eva}{\textcolor{gray}{Dr. Eva
      Darulová}}}
  {
  \item Developed, evaluated a Scala tool to rewrite
    mathematical floating-point expressions and increase their
    accuracy using a genetic algorithm.
  \item Decreased floating point errors in expressions by
    \~$50\%$, useful for scientific and embedded uses.
  }

  \expitem{Full Stack Developer}{May'15-Apr'16}
  {NYC Office IIT Kanpur,
    \href{http://cse.iitk.ac.in/~manindra}{\textcolor{gray}{Prof. Manindra Agarwal}}}
  {
  \item Worked on a large-scale microservice based web
    application with an extensive and polyglot stack.
  \item Implemented critical backend functionality, including program evaluation, attachment support.
  \item Designed, implemented and deployed the full search functionality using Scala, ElasticSearch, TypeScript.
  }
\end{experience}

\vspace{-1.0cm}

\section{Education}
\begin{yearlist}
\item[Computer Science, IIT Kanpur]{\small{2014--Now}}
  {Bachelor of Technology}
  {\textbf{CGPA: 10.0/10.0}}
\end{yearlist}

\vspace{-0.4cm}
\section{Awards and Achievements}

\begin{yearlist}

\item{\small{Now}}
  {Institute Rank \textbf{1}, IIT Kanpur}
  {\small{SPI/GPA: 10.0 in all 6 Semesters}}

\item{\small{2016}}
  {Academic Excellence Award}
  {\small{IIT Kanpur, 2015 and 2016}}

\item{\small{2014}}
  {All India Rank \textbf{10}}
  {\small{JEE Mains, 1.5 million candidates}}

\item {\small{2014}}
  {All India Rank \textbf{138}}
  {\small{JEE Advanced, 150,000 candidates}}

\item {\small{2014}}
  {Aditya Birla Scholarship}
  {\small{Among 15 top students from all IITs}}

\item {\small{2014}}
  {National Merit, Overall \textbf{97.6\%}}
  {\small{Grade 12/High School, CBSE}}

\item {\small{2013}}
  {KVPY Scholarship awardee}
  {\small{Scholarship by IISc, Govt. of India}}

\item {\small{2010}}
  {National Talent Search (NTS)}
  {\small{Scholarship by Govt. of India}}

\end{yearlist}

\vspace{-0.3cm}

\needspace{0.5\textheight}
\newdimen\boxwidth
\boxwidth=\dimexpr\linewidth-2\fboxsep\relax
\colorbox[HTML]{F5DD9D}{
  \begin{tabularx}{\boxwidth}{c|l}
    {\faEnvelope} &
    \href{mailto:saksham0808@gmail.com}{saksham0808@gmail.com}\\
    {\faRss} & \href{http://sakshamsharma.com}{sakshamsharma.com}\\
    {\faGithub} &
    \href{https://github.com/sakshamsharma}{sakshamsharma}\\
    % {\faMobile} &
    % \href{tel:+917755058004}{+91-7755058004}\\
  \end{tabularx}}

\vspace{-0.1cm}

\section{Projects}
\begin{experience}
  \expitem{Tipsy: Tool to provide tips and corrections for C programs en masse}{}
  {Undergraduate project, {\href{http://cse.iitk.ac.in/~karkare}{Prof. Amey Karkare}}}
  {
    \item Created a tool in Scala to analyze and cluster C programs from large programming courses, to provide tips to weak students.
    \item Reduced C programs to a linear high level representation, which was later used for finding shortest distance between 2 programs.
    \item Tool provides corrections and hints based on similar programs in the corpus.
  }

  \expitem{\href{https://github.com/pclubiitk/puppy-love}{\linkbold{Anonymous and
        secure couple-matching}}}{}
  {\href{http://cse.iitk.ac.in/~ppk}{Prof. P. Kurur},
    \href{http://cse.iitk.ac.in/~satyadev}{\textcolor{gray}{Prof. S. Nandakumar}}}
  {
    \vspace{0.1cm}
  \item Designed, implemented an algorithm
    for completely anonymous matching of couples, where end users put
    zero trust in the server (admin) and its code.
  \item Use Diffie Hellman inspired secure two party computation to
    ensure confidentiality and integrity.
    \item Deployed on campus, used by \~1800 users.
  }

  \expitem{Amigo: A 4-stage x64 Compiler for Golang}{}
  {Course project, {\href{http://cse.iitk.ac.in/~karkare}{Prof. Amey Karkare}}}
  {
    \item Implemented a compiler for a fully functional subset of the Go language, in C++ and Python.
    \item Used flex and bison to obtain an AST, which is later translated to a x64 assembly.
    \item Implemented pointers, multiple return values, deeply nested arrays, among other features; along with some low level optimizations.
  }
\end{experience}

\vspace{-0.7cm}
\section{Coursework}
\begin{inlinelist}
\item Operating Systems \astar
\item Compiler Design \astar\\
\item Modern Cryptology \astar
\item Systems Security\\
\item Computer Organization \astar
\item Algorithms \astar
\item Computer Networks \astar
\item Computer Architecture
\item Introduction to programming \astar
\end{inlinelist}\\
{\small A*: grade for exceptional performance\par}

\vspace{-0.4cm}
\section{Technical Skills}

\begin{factlist}
\item{\small{Langs}}
  {C/C++, Go, Scala, Python, Node.js}

\item{\small{Web}}
  {Express.js, Akka, TypeScript, Angular}

\item {\small{Utils}}
  {Git, Kubernetes, ElasticSearch}

\end{factlist}

\vspace{-0.3cm}
\section{Miscellaneous}
\vspace{0.2cm}
\begin{thinitemize}
\item Won \textbf{Microsoft code.fun.do} hackathon \textbf{twice}.
\item \textbf{Coordinator} of Programming Club \& InfoSec; organized
  contests, CTFs, lectures (\href{http://pclub.in}{pclub.in}).
\item Administer \textbf{servers} in IIT Kanpur; deploying,
  automating services for campus community.
\item Microsoft Build The Shield, National 10th in the final round of
  \textbf{CTF}.
\end{thinitemize}

\end{document}

%%% Local Variables:
%%% mode: xelatex
%%% TeX-engine: xetex
%%% TeX-master: t
%%% End:
