% ----------------------------------------------------------------------------------------
% SECTION TITLE
% ----------------------------------------------------------------------------------------

\vspace{-0.2cm}
\cvsection{Work Experience}

% ----------------------------------------------------------------------------------------
% SECTION CONTENT
% ----------------------------------------------------------------------------------------

\begin{cventries}

  % ------------------------------------------------
  \cventry
  {Low Latency Software Developer}
  {Limestone Trading Team, Tower Research Capital}
  {Gurgaon, India}
  {Jul. 2018 - Present}
  {
    \begin{cvitems}
    \setlength\itemsep{0.1cm}
    \item {Work as a Quantitative Research developer, writing high performance algorithmic trading systems in C++, which run the core trading strategies of the team across trading venues.}
    \item {Develop software in C++ and Python which allow the trading team to scale strategies and research across exchanges and products, while remaining competitive in terms of speed.}
    \end{cvitems}
  }

  \cventry
  {Software Engineering Intern, Google Cloud}
  {GKE/Kubernetes Security Team, Google Seattle}
  {Seattle, WA}
  {May. 2017 - Jul. 2017}
  {
    \begin{cvitems}
    \setlength\itemsep{0.1cm}
    \item {Worked on Kubernetes, Google's open source Docker container orchestration platform, to encrypt resources in cluster database at rest, a feature requested by industry for security hardening.}
    \item {Implemented envelope encryption using Key-Encryption-Keys and Data-Encryption-Keys to allow using remote cloud-based Key Management Services.}
    % \item {Designed a method for allowing key rotations in a multi-master system with a shared database.}
    \item {Feature released as alpha in v1.7, integration with Google's Key Management System and others is upcoming.}
    \item {Collaborated with engineers across multiple companies. Received a returning job offer.}
    \end{cvitems}
  }

  \cventry
  {research Fellow, under Dr. Eva Darulová} % Job title
  {Max Planck Institute for Software Systems} % Organization
  {Saarbrücken, Germany} % Location
  {May. 2016 - Jul. 2016} % Date(s)
  {
    \begin{cvitems}
    \setlength\itemsep{0.1cm}
    \item {Developed and evaluated a Scala tool to rewrite
    mathematical floating-point expressions and increase their
    accuracy using a genetic algorithm.}
    \item {Obtained successful results, improving expression errors by
    $\textasciitilde50\%$, for scientific and embedded
    applications.}
    \item {\textbf{In proceedings} of the 9th ACM/IEEE International Conference on Cyber-Physical Systems.}
    \end{cvitems}
  }

  \cventry
  {Full Stack Developer, under Prof. Manindra Agarwal}
  {New York Office, IIT Kanpur}
  {Kanpur, India}
  {May. 2015 - Apr. 2016}
  {
    \begin{cvitems}
    \setlength\itemsep{0.1cm}
    \item Worked on a scalable microservice based web application with an extensive technology stack.
    \item Designed and developed critical backend features while
      ensuring type-safety.
    \item Developed and deployed the complete search functionality
      (using ElasticSearch, Scala, TypeScript).
    \end{cvitems}
  }

  % ------------------------------------------------
\end{cventries}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../resume_twopage.tex"
%%% End:
